THESIS TITLE

### 2023-07-03 theory.tex
theory mostly done

\subsection{Relation between momentum and acceleration}
In classical mechanics, Newton's second law defines momentum and states 
\begin{equation}
    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
\end{equation}
In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where gamma is the Lorentz Factor;
\begin{equation*}
    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
\end{equation*}
Considering these two statements, we can find the relation between momentum and acceleration as follows
\begin{eqnarray*}
    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
\end{eqnarray*}
\begin{equation} \label{eq:Frel}
    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
\end{equation}
It is clear that acceleration is not necessarily parallel to the force. To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
\begin{equation} \label{eq:a_F_parallels}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
    \end{aligned}
\end{equation}
\begin{eqnarray*}
    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
\end{eqnarray*}
Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
\begin{equation*}
    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
\end{equation*}
Inserting this
\begin{eqnarray}
    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
\end{eqnarray}
Therefore from \fromeqs{Frel}{Frel_parallel}
\begin{eqnarray*}
    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
\end{eqnarray*}
\begin{equation} \label{eq:Frel_para_and_perp}
    \begin{aligned}
        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
    \end{aligned}
\end{equation}

\subsection{Lorentz Force}
Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
\newline
\begin{equation} \label{eq:lf}
    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
\end{equation}
\newline
where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.

\subsection{Relativistic Lorentz Force}
Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
\begin{equation}
    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
\end{equation}
Where $ \partial \tau = \partial t / \gamma $,
\begin{equation}
    \begin{aligned}
        p^{\mu} = 
        \begin{bmatrix}
            W/c \\
            p_x         \\
            p_y \\
            p_z
        \end{bmatrix}    
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        F^{\mu\nu} = 
        \begin{bmatrix}
                0       & -E_x/c   & -E_y/c    & -E_z/c \\
                E_x/c   &   0      & -B_z      & B_y     \\
                E_y/c   &   B_z    &  0        & -B_x     \\
                E_z/c   &   -B_y   & B_x       & 0   
        \end{bmatrix} 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        u_{\nu} = \gamma
        \begin{bmatrix}
                 c \\
                -v_x \\
                -v_y \\
                -v_z \\
        \end{bmatrix} 
    \end{aligned}
\end{equation}
Where $W$ is the energy of the particle and $\gamma = 1 / \sqrt{1 - v^2 / c^2}$ is the lorentz factor.
\newline

@@

\subsection{Acceleration caused by lorentz force}
Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
Therefore the acceleration of the magnetic field is straightforward
\begin{equation*}
    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
\end{equation*}
The same thing cannot be said about electric field however. 
It can create force in any direction with respect to velocity. Therefore, we have the following equality;
\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
    \end{aligned}    
\end{equation}
Acceleration due to electric field can be simplified as;
\begin{eqnarray*}
    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
\end{eqnarray*}
Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
\begin{equation} \label{eq:acc_of_E_and_B}
    \begin{aligned}
        \vecthreeBF{a}_{E} = \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
    \end{aligned}
\end{equation}

\newpage
\section{Practical}

\subsection{Accelerators}
Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.

@@

\begin{equation} \label{eq:general-rk}
    \begin{aligned}
        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
    \end{aligned}
    \qquad
    \begin{aligned}
        x_{n+1} = x_n + \delta x 
    \end{aligned}
\end{equation}

where

\begin{eqnarray} \label{eq:general-rk-coef}
    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
\end{eqnarray}

@@

The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.

\[ 
    \begin{array} 
        {c|cccc}
        0\\
        \hline
        & 1
    \end{array}
\]

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}{}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/2 & 1/2 \\
            1/2 & 0 & 1/2 \\
            1   & 0 & 0 & 1\\
            \hline
            & 1/6 & 1/3 & 1/3 & 1/6
        \end{array}
        \]  
    \end{subfigure} %
    \centering
    \begin{subfigure}{}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/3 & 1/3 \\
            2/3 & -1/3 & 1 \\
            1   & 1 & -1 & 1\\
            \hline
            & 1/8 & 3/8 & 3/8 & 1/8
        \end{array}
        \]  
    \end{subfigure}
    \caption{Butcher Tableau for RK4}
    \label{fig:Butcher-RK4}
\end{figure}

@@

Simulation software provides a virtual environment where users can define the parameters,
variables, and rules of the system being simulated. The software then uses mathematical models, 
algorithms, and computational techniques to simulate the behavior of the system over time.

\subsection{}

>>>>

\subsection{Relation between momentum and acceleration}
In classical mechanics, Newton's second law defines force and states 
\begin{equation} \label{eq:newton_second_law}
    \vecthreeBF{F} = \frac{\partial \vecthreeBF{p}}{\partial t} = m \frac{\partial \vecthreeBF{v}}{\partial t} = m \vecthreeBF{a}
\end{equation}
In special relativity however, relativistic momentum is defined as $\vecthree{p} = \gamma m_0 \vecthree{v} $ where $\gamma$ is the Lorentz Factor;
\begin{equation*}
    \gamma = \frac{1}{\sqrt{1-v^2 / c^2}} = \frac{1}{\sqrt{1-\beta^2}}
\end{equation*}
Considering these two statements, we can find the relation between momentum and acceleration as follows
\begin{eqnarray*}
    \parDeriv{\vecthree{p}}{t} &=& m_0 \parDeriv{(\gamma \vecthree{v})}{t} = m_0 \{  \parDeriv{\gamma}{t}\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} \\
    \parDeriv{\gamma}{t} &=& \gamma^3 \dotProd{\beta}{\parDeriv{\beta}{t}} = \frac{\gamma^3}{c} \dotProd{\beta}{a} \\
    \parDeriv{\vecthree{p}}{t}  &=& m_0 \{   \frac{\gamma^3}{c} (\dotProd{\beta}{a} )\vecthree{v} + \gamma \parDeriv{\vecthree{v}}{t}  \} 
\end{eqnarray*}
\begin{equation} \label{eq:Frel}
    \vecthreeBF{F}  = \gamma m_0 \{ \vecthreeBF{a} + \gamma^2(\dotProd{\beta}{\textbf{a}})\vecthree{\beta} \}
\end{equation}
It is clear that acceleration is not necessarily parallel to the force anymore. To start seperating the parallel and perpendicular components relative to $\vecthree{\beta}$, we can find $\vecthreeBF{a}_{||}$ and  $\vecthreeBF{F}_{||}$;
\begin{equation} \label{eq:a_F_parallels}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{(\dotProd{a}{\beta})}{\beta^2}\beta 
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{||} = \frac{(\dotProd{F}{\beta})}{\beta^2}\beta 
    \end{aligned}
\end{equation}
\begin{eqnarray*}
    \dotProd{\textbf{F}}{\beta} &=& \gamma m_0 \{ \dotProd{\textbf{a}}{\beta} + \gamma^2(\dotProd{\beta}{\textbf{a}})\beta^2 \} \\
                                &=& \gamma m_0 (\dotProd{\textbf{a}}{\beta}) \{ \gamma^2\beta^2  + 1\} 
\end{eqnarray*}
Using $\gamma^2 \beta^2 + 1 = \gamma^2 $ we have,
\begin{equation*}
    \dotProd{\textbf{F}}{\beta} = m_0 \gamma^3 (\dotProd{\textbf{a}}{\beta} )
\end{equation*}
Inserting this
\begin{eqnarray}
    \vecthreeBF{F}_{||} &=& \frac{(\dotProd{\textbf{F}}{\beta})}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \frac{(\dotProd{\textbf{a}}{\beta} )}{\beta^2} \vec{\beta} \nonumber \\
                        &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \label{eq:Frel_parallel}
\end{eqnarray}
Therefore from \fromeqs{Frel}{Frel_parallel}
\begin{eqnarray*}
    \vecthreeBF{F}  &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \vecthreeBF{a} \\
                    &=& m_0 \gamma^3 \vecthreeBF{a}_{||} \beta^2 + m_0 \gamma \{ \vecthreeBF{a}_{||} +  \vecthreeBF{a}_{\perp} \} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma \{ \gamma^2\beta^2 + 1 \} + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& m_0 \vecthreeBF{a}_{||} \gamma^3 + m_0 \gamma \vecthreeBF{a}_{\perp} \\
                    &=& \vecthreeBF{F}_{||} + m_0 \gamma \vecthreeBF{a}_{\perp}
\end{eqnarray*}
We finally have two seperate equations which are in similar form with \fromeq{newton_second_law}.
\begin{equation} \label{eq:Frel_para_and_perp}
    \begin{aligned}
        \vecthreeBF{F}_{||} = \gamma^3  m_0 \vecthreeBF{a}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp}
    \end{aligned}
\end{equation}

\subsection{Lorentz Force} \label{sec:lorentz-force}
Force acting on a charged particle moving in electromagnetic fields is called Lorentz Force and is given by the formula
\newline
\begin{equation} \label{eq:lf}
    \frac{\partial \vecthree{p}}{\partial t} = \vecthree{F}_L=q(\vecthree{E}+ \vecthree{v} \times \vecthree{B})
\end{equation}
\newline
where the $q$ is the charge and $\vecthree{v}$ is the velocity of the particle.

\subsection{Relativistic Lorentz Force}
Similar to non-relativistic version, relativistic Lorentz Force is given by the following 4-vector equality
\begin{equation}
    \frac{\partial p^{\mu}}{\partial \tau} = q F^{\mu \nu} u_{\nu}
\end{equation}
Where $ \partial \tau = \partial t / \gamma $,
\begin{equation}
    \begin{aligned}
        p^{\mu} = 
        \begin{bmatrix}
            W/c \\
            p_x         \\
            p_y \\
            p_z
        \end{bmatrix}    
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        F^{\mu\nu} = 
        \begin{bmatrix}
                0       & -E_x/c   & -E_y/c    & -E_z/c \\
                E_x/c   &   0      & -B_z      & B_y     \\
                E_y/c   &   B_z    &  0        & -B_x     \\
                E_z/c   &   -B_y   & B_x       & 0   
        \end{bmatrix} 
    \end{aligned}
    \qquad\qquad
    \begin{aligned}
        u_{\nu} = \gamma
        \begin{bmatrix}
                 c \\
                -v_x \\
                -v_y \\
                -v_z \\
        \end{bmatrix} 
    \end{aligned}
\end{equation}
Where $W$ is the energy of the particle and $\gamma$ is the lorentz factor mentioned in the previous section.
\newline

@@

\subsection{Acceleration caused by lorentz force}
Due to the nature of the cross product, lorentz force caused by a magnetic field is always perpendicular to the velocity of the particle. 
Therefore the acceleration of the magnetic field is straightforward
\begin{equation*}
    \vecthreeBF{F}_B = \vecthreeBF{F}_{\perp} = \gamma  m_0\vecthreeBF{a}_{\perp} = \gamma  m_0\vecthreeBF{a}_{B}
\end{equation*}
The same thing cannot be said about electric field however. 
It can create force in any direction with respect to velocity. Therefore, we have the following equality;
\begin{equation} \label{eq:para_and_perp_acc_of_lorentz_force}
    \begin{aligned}
        \vecthreeBF{a}_{||} = \frac{q }{\gamma^3 m_0} \vecthreeBF{E}_{||}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{\perp} = \frac{q}{\gamma m_0} \{ \vecthreeBF{E}_{\perp} + \crossProdBF{v}{B}   \}
    \end{aligned}    
\end{equation}
Acceleration due to electric field can be simplified as;
\begin{eqnarray*}
    \vecthreeBF{a}_{\{B=0\}} = \vecthreeBF{a}_{E}   &=&  \vecthreeBF{a}_{||} + \vecthreeBF{a}_{\perp \{B=0\}} \\
                                &=& \frac{q}{m_0 \gamma} \{ \frac{\vecthreeBF{E}_{||}}{\gamma^2} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \{1 - \beta^2\}\vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E}_{||} + \vecthreeBF{E}_{\perp}-\beta^2\vecthreeBF{E}_{||} \} \\
                                &=& \frac{q}{m_0 \gamma} \{ \vecthreeBF{E} - \beta^2\vecthreeBF{E}_{||} \} \\
\end{eqnarray*}
Using the fact that $\vecthreeBF{E}_{||} = \vec{\beta}(\dotProd{\textbf{E}}{\beta})/\beta^2 $, we finally have
\begin{equation} \label{eq:acc_of_E_and_B}
    \begin{aligned}
        \vecthreeBF{a}_{E} = \frac{q}{ \gamma m_0} \{ \vecthreeBF{E} - \vecthreeBF{v}\frac{(\dotProdBF{E}{v})}{c^2} \}
    \end{aligned}
    \qquad \qquad
    \begin{aligned}
        \vecthreeBF{a}_{B} = \frac{q}{\gamma m_0} ( \crossProdBF{v}{B} )
    \end{aligned}
\end{equation}

\newpage
\section{Particle Accelerators}

Particle accelerators are sophisticated scientific instruments designed to accelerate charged particles, such as electrons, protons, or ions, to high speeds and energies. 
These accelerators play a crucial role in advancing our understanding of the fundamental properties of matter and the universe. 
They are widely used in various fields of research, including particle physics, nuclear physics, materials science, and medicine.

@@

\begin{equation} \label{eq:general-rk}
    \begin{aligned}
        y_{n+1} = y_n + \delta x \sum_{i=1}^{m} b_i k_i
    \end{aligned}
    \qquad
    \begin{aligned}
        x_{n+1} = x_n + \delta x 
    \end{aligned}
\end{equation}
where 
\begin{eqnarray} \label{eq:general-rk-coef}
    k_i = f(x_n + c_i \delta x, y_n + \delta x \sum_{j = 1}^{i - 1}a_{ij}k_j)
\end{eqnarray}

@@

The simplest Runge-Kutta method is the \textit{Euler's method}. Its \textit{Butcher tableau} is as follows.
\[ 
    \begin{array} 
        {c|cccc}
        0\\
        \hline
        & 1
    \end{array}
\]

@@

\begin{figure}[h!]
    \centering
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/2 & 1/2 \\
            1/2 & 0 & 1/2 \\
            1   & 0 & 0 & 1\\
            \hlinevvmwa
            & 1/6 & 1/3 & 1/3 & 1/6
        \end{array}
        \]  
    \end{subfigure}%
    \begin{subfigure}{.5\textwidth}
        \[ 
        \begin{array} 
            {c|cccc}
            0\\
            1/3 & 1/3 \\
            2/3 & -1/3 & 1 \\
            1   & 1 & -1 & 1\\
            \hline
            & 1/8 & 3/8 & 3/8 & 1/8
        \end{array}
        \]  
    \end{subfigure}
    \caption{Butcher Tableau for RK4}
    \label{fig:Butcher-RK4}
\end{figure}

@@

Simulation software provides a virtual environment where users can define the parameters,
variables, and rules of the system being simulated. The software then uses mathematical and physical models, 
algorithms, and computational techniques to simulate the behavior of the system over time.

\subsection{Basic Consepts in Programming}

\subsubsection{Clock Cycle}

In programming, a clock cycle refers to a fundamental unit of time measurement used in computer systems. 
It represents the basic rhythm or timing mechanism of a computer's central processing unit (CPU) and is typically measured in terms of the CPU's clock speed, expressed in hertz (Hz).

A clock cycle represents one complete pulse or oscillation of the CPU's clock signal. 
It serves as a synchronization mechanism, coordinating the execution of instructions and the timing of various operations within the CPU.
Each clock cycle is associated with a specific duration, which is determined by the clock speed of the CPU.

The concept of clock cycles is often used when considering the performance and efficiency of algorithms and code. 
Since the execution time of instructions is influenced by the number of clock cycles required, minimizing the number of clock cycles needed for a program or algorithm can lead to faster and more efficient code execution.
Table below shows the amount of clock cycles required for some mathematical calculations in various processors.

\begin{figure}[h!]
    \centering
    \includegraphics[width=.9\textwidth]{./figures/cpu_instruction_speed.png}
    \caption{Amount of clock cycle for mathematical operations in various processors. \cite{cpu_instruction_speed}}
\end{figure}

Note that \textit{division} is by far the most time consuming basic mathematical operation between addition, subtraction and multiplication.

\subsubsection{Concurrency}

Concurrency in programming refers to the ability of a program to execute multiple tasks or processes simultaneously. It allows different parts of a program to make progress independently, potentially improving performance, responsiveness, and resource utilization.

Concurrency in single core can be achieved by implementing clever scheduling of list of operations called \textit{threads}. This results in non-blocking execution of multiple threads, but only one thread would be executed at any given time. 
True concurrency on the other hand, can only be achieved by using multiple cores. Each core would be able to execute one thread at any time.

Programs that implement concurrency using multiple cores executes more operations per clock cycle. However, this does not directly lead to an improved performance due to the heavy burden of scheduling and managing multiple threads.

\begin{thebibliography}{9}

    \bibitem{rhodo_pottier}
    Jacques Pottier,
    \emph{A new type of rf electron accelerator: The rhodotron},
    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
    Volumes 40–41, Part 2,
    1989,
    Pages 943-945,

    \bibitem{rhodo_prototype}
    J.M. Bassaler, J.M. Capdevila, O. Gal, F. Lainé, A. Nguyen, J.P. Nicolaï, K. Umiastowski,
    \emph{Rhodotron: an accelerator for industrial irradiation},
    Nuclear Instruments and Methods in Physics Research Section B: Beam Interactions with Materials and Atoms,
    Volume 68, Issues 1–4,
    1992,
    Pages 92-95,A:

    \bibitem{rhodos}
    Y. Jongen. (2001). \emph{Manufacturing of Electron Accelerators}. Ion Beam Applications s.a. (IBA) Chemin du Cyclotron 3, B-1348 Louvain-la-Neuve, Belgium.

    \bibitem{cpu_instruction_speed}
    Fukushima, Toshio. (2001). \emph{Reduction of Round-off Errors in Symplectic Integrators}. The Astronomical Journal. 121. 1768-1775.

\end{thebibliography}
